\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-29 notes/2loopNLSM.tex
Added paragraph about hypothetical minimal failure state.  Need to check it.

>>>>

\ace{I need to check this.  For now it is a standing hypothesis:} In
fact, we can make the failure extremely precise.  Start with the
diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
the double-box, crossed-box, and penta-triangle.  For each of the
three diagrams, write down the most generic parity-even local ansatz
involving four polarizations and six momenta (any combination of external or loop).  Each ansatz will be
10,010 terms initially.  Next impose the symmetry constraints on each
of the three diagrams, leaving XX free parameters on the double-box,
YY free parameters on the crossed-box, and ZZ free paramters on the
penta-triangle.  Then impose the ``kissing triangle'' next-to-maximal
cut, which in the \emph{non-planar} color channel only recieves
contributions from the double-box
\begin{equation}
  \KissingTriangles
  =
  \frac{1}{(\textcolor{nhp4}{\ell_1})^2} \
  n \left[
    \DoubleBoxLabeled{1}{2}{3}{4}
  \right]
  +
  \frac{1}{(\textcolor{nhp4}{\ell_2})^2} \
  n\left[\DoubleBoxLabeled{1}{3}{2}{4}\right]
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{equation}
  \KissingTriangles
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0
\end{equation}
